---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pfoliokitr

<!-- badges: start -->
<!-- badges: end -->

pfoliokitr is a small toolkit for fetching stock price data, computing
returns, and evaluating performance and risk for stocks and benchmarks.
Built on top of `quantmod`, `PerformanceAnalytics`, and `xts`.

## Installation

You can install the development version of pfoliokitr like so:

``` r
devtools::install_github("yvescandoit/pfoliokitr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(pfoliokitr)

lly <- tckr_data("LLY", from = "2021-04-01")
spy <- tckr_data("SPY", from = "2021-04-01")

lly_ret <- log_ret(lly)
spy_ret <- log_ret(spy)

metrics(lly_ret,0.05)
relative_metrics(lly_ret,spy_ret)
```


## What's included

- **`tckr_data()`** — fetch adjusted close prices for a ticker
- **`log_ret()`** — compute daily log returns
- **`aligned_returns()`** — align two return series on shared dates
- **`metrics()`** — annualised return, volatility, Sharpe, Sortino, Calmar, max drawdown, skewness, kurtosis
- **`risk_metrics()`** — VaR / CVaR, switchable between historical, Gaussian, and modified (Cornish-Fisher) methods
- **`bootstrap_returns()`** — block bootstrap simulation for multi-day risk estimates
- **`relative_metrics()`** — beta and alpha vs. a benchmark
- **`combine_metrics()` / `print()` / `as.data.frame()`** — merge, display, and export results

See `vignette("pfoliokitr-walkthrough")` for a full walkthrough.



