---
title: "pfoliokitr-walkthrough"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pfoliokitr-walkthrough}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette walks through the whole pfoliokitr pipeline: fetching price data, computing returns,
checking the shape of the return distribution, computing performance and risk metrics and comparing a 
stock vs benchmark.

## 1. Fetch the adjusted price data

`tckr_data()` fetches historical prices for a ticker and returns just the adjusted close series,
which accounts for dividents and splits.

```{r}
library(pfoliokitr)

lly <- tckr_data("LLY", from = "2020-01-01")
spy <- tckr_data("SPY", from = "2020-01-01")

head(lly)
head(spy)
```


## 2. Compute daily log returns 

`log_ret()` converts a price series into log returns.

```{r}

lly_ret <- log_ret(lly)
spy_ret <- log_ret(spy)

head(lly_ret)
```


## 3. Compute Performance metrics and check the shape of distribution


`metrics()` computes a full set of standalone performance metrics for areturn series
— annualised return, annualised volatility, Sharpe ratio, Sortino ratio, 
Calmar ratio, and max drawdown — along with skewness and excess kurtosis,
which describe the shape of the return distribution.

```{r}
lly_metrics <- metrics(lly_ret, 0.05)   #risk free rate of US
lly_metrics
```

The skewness and kurtosis values are worth to look at before computing the risk metrics in
the next step. Returns which are close to normal (Skew near 0, low excess kurtosis) make a 
Gaussian VaR estimate reasonable. 

Fat tails or strong skew mean a Gaussian assumption will likely understate the real risk hidden in 
the tails for which either historical or modified (Corner-Fisher) is preferred instead.

```{r}
lly_metrics$skewness
lly_metrics$kurtosis
```

## 4. Compute risk metrics

`risk_metrics()` supports three distributional assumptions, chosen using the diagnostic above.

```{r}
risk_metrics(lly_ret, 0.95, method = "gaussian")
risk_metrics(lly_ret, 0.95, method = "historical")
risk_metrics(lly_ret, 0.95, method = "modified")
```

### A note on VaR/CVaR horizon

The metrics above show only the **1-day** VaR/CVaR estimates. For longer time horizon 
`bootstrap_ret()` simulates multi-day returns via block resampling, which avoids the 
common (and often in-accurate) scaling of 1-day VaR by `sqrt(n)`.

```{r}
lly_10day_sim <- bootstrap_ret(lly_ret, 10, 10000)
risk_metrics(lly_10day_sim, 0.95, "historical")
```

Note this is a **10-day** estimate and isn't directly comparable to the above metrics figures.


##. 5 Compute metrics relative to the benchmark.

`relative_metrics()` aligns the stock and benchmark on shared dates internally, so raw 
unaligned return series can be passed in directly.

```{r}
relative_metrics(lly_ret, spy_ret,0.05)
```

Note this is a **10-day** estimate and isn't directly comparable to the 1-day figures above.

##. 6 Combine everything into one summary.

`combine_metrics` merges combination of `metrics()`, `risk_metrics()` & `relative_metrics` 
output into a single object. which prints all of it together.

```{r}
full_summary <- combine_metrics(
  metrics(lly_ret, 0.05),
  risk_metrics(lly_ret, 0.95, "historical"),
  relative_metrics(lly_ret,spy_ret)
)

print(combine_metrics,label = "LLY")
```

##. 7 Export it for further analysis.

Any `portfolio_metrics` can be converted into a data frame, e.g. for creating a table across several stocks:

```{r}
as.data.frame(full_summary)
```

